Evaluation of performances

### 2021-11-06 analysis/eval-performance.Rmd
chmod 644 -> 755

results_aggr %>%
  ggplot(aes(x = rmse_aggr, y = task.id)) +
  # geom_jitter(aes(color = learner_group), size = 2, width = 0, height = 0.3) +
  # geom_dotplot(aes(fill = learner_group), binaxis="y",
  #                        stackdir="up") +
  ggbeeswarm2::geom_beeswarm(groupOnX = FALSE, aes(color = learner_group), size = 2.5) +
  # scale_color_nejm(breaks = sort(levels(results_aggr$learner_group))) +
  # scale_color_viridis_d(breaks = sort(levels(results_aggr$learner_group))) +
  scale_color_viridis_d(breaks = results_aggr$learner_group) +
  labs(x = "RMSE", y = "Task", color = "Learner") +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(27, 40), breaks = seq(28, 40, 2)) +
  geom_label_repel(
    # subset data to remove out of bounds values
    data = results_aggr[results_aggr$rmse_aggr < 100, ],
    # from ggbeeswarm, avoid overlapping of points by labels
    position = position_quasirandom(),
    aes(label = paste0(filter, ",", round(rmse_aggr, 3))),
    size = 4,
    min.segment.length = 0.1,
    seed = 123,
    point.padding = 0.5
  ) +
  theme_pubr(base_size = 14) +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 13),
    axis.text.y = element_text(angle = 45),
    plot.margin = unit(c(6, 6, 6, 0), "pt")
  )
```

>>>>

results_aggr %>%
  ggplot(aes(x = rmse_aggr, y = task.id)) +
  # geom_jitter(aes(color = learner_group), size = 2, width = 0, height = 0.3) +
  # geom_dotplot(aes(fill = learner_group), binaxis="y",
  #                        stackdir="up") +
  ggbeeswarm2::geom_beeswarm(groupOnX = FALSE, aes(color = learner_group), size = 2.5) +
  # scale_color_nejm(breaks = sort(levels(results_aggr$learner_group))) +
  # scale_color_viridis_d(breaks = sort(levels(results_aggr$learner_group))) +
  scale_color_viridis_d(breaks = results_aggr$learner_group) +
  labs(x = "RMSE", y = "Task", color = "Learner") +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(27, 40), breaks = seq(28, 40, 2)) +
  geom_label_repel(
    # subset data to remove out of bounds values
    data = results_aggr[results_aggr$rmse_aggr < 100, ],
    # from ggbeeswarm, avoid overlapping of points by labels
    position = position_quasirandom(),
    aes(label = paste0(filter, ",", round(rmse_aggr, 2))),
    size = 4,
    min.segment.length = 0.1,
    seed = 123,
    point.padding = 0.5
  ) +
  theme_pubr(base_size = 14) +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 13),
    axis.text.y = element_text(angle = 45),
    plot.margin = unit(c(6, 6, 6, 0), "pt")
  )
```
